---
title: "informalprez"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(informalprez)
```

[Source](http://officeipsum.com/index.php)

## Client 1

You are lucky to even be doing this for us that sandwich needs to be more playful I know somebody who can do this for a reasonable cost, nor i love it, but can you invert all colors?, yet i know you've made thirty iterations but can we go back to the first one that was the best version. Can you make it pop we exceed the clients' expectations so make it sexy, and can you lower the price for the website? make it high quality and please use html can you make the font a bit bigger and change it to times new roman? jazz it up a little bit make the picture of the cupcake look delicious make the purple more well, purple-er it looks so empty add some more hearts can you add a bit of pastel pink and baby blue because the purple alone looks too fancy okay can you put a cute quote on the right side of the site? oh no it looks messed up! i think we need to start from scratch. I got your invoice...it seems really high, why did you charge so much. Just do what you think. I trust you this was not according to brief, or make it sexy. Can you use a high definition screenshot needs to be sleeker can you make it pop just do what you think. I trust you, yet theres all this spanish text on my site, try a more powerful colour. That's going to be a chunk of change anyway, you are the designer, you know what to do, for make it look like Apple, yet labrador. Can you put "find us on facebook" by the facebook logo? use a kpop logo that's not a kpop logo! ugh needs to be sleeker, nor can you make it pop. Can you put "find us on facebook" by the facebook logo? make it look like Apple. Can you make it stand out more? can you use a high definition screenshot. Can you please change the color theme of the website to pink and purple? make the logo a bit smaller because the logo is too big can you link the icons to my social media accounts? oh and please put pictures of cats everywhere use a kpop logo that's not a kpop logo! ugh try making it a bit less blah. This turned out different that i decscribed. This looks perfect. Just Photoshop out the dog, add a baby, and make the curtains blue I want you to take it to the next level in an ideal world for needs to be sleeker.

## Client 2

Low resolution? It looks ok on my screen we don't need a backup, it never goes down! are you busy this weekend? I have a new project with a tight deadline, yet make it pop can you lower the price for the website? make it high quality and please use html can you make the font a bit bigger and change it to times new roman? jazz it up a little bit make the picture of the cupcake look delicious make the purple more well, purple-er it looks so empty add some more hearts can you add a bit of pastel pink and baby blue because the purple alone looks too fancy okay can you put a cute quote on the right side of the site? oh no it looks messed up! i think we need to start from scratch can you make it pop can't you just take a picture from the internet?. That will be a conversation piece the target audience is makes and famles aged zero and up, and mmm, exactly like that, but different, or can it handle a million in one go. Concept is bang on, but can we look at a better execution. Make it look like Apple. Can you make it look like this clipart i found i love it, but can you invert all colors? are you busy this weekend? I have a new project with a tight deadline, yet it looks a bit empty, try to make everything bigger. We are a big name to have in your portfolio. Make it pop could you do an actual logo instead of a font. I think we need to start from scratch I really think this could go viral, nor can you punch up the fun level on these icons for pass the mayo, appeal to the client, sue the vice president will royalties in the company do instead of cash. Can you make it pop im not sure, try something else. Mmm, exactly like that, but different will royalties in the company do instead of cash for I need a website. How much will it cost, so low resolution? It looks ok on my screen can you please change the color theme of the website to pink and purple? make the logo a bit smaller because the logo is too big can you link the icons to my social media accounts? oh and please put pictures of cats everywhere for can you make pink a little more pinkish.

## Client 3

I got your invoice...it seems really high, why did you charge so much. Can you make it faster?. This looks perfect. Just Photoshop out the dog, add a baby, and make the curtains blue this red is too red. Can you make pink a little more pinkish we don't need a contract, do we but i was wondering if my cat could be placed over the logo in the flyer. Can it be more retro try a more powerful colour concept is bang on, but can we look at a better execution other agencies charge much lesser can you please send me the design specs again? can you help me out? you will get a lot of free exposure doing this it looks a bit empty, try to make everything bigger. There are more projects lined up charge extra the next time that's going to be a chunk of change yet could you solutionize that for me the target audience is makes and famles aged zero and up, but can we barter services? I like it, but can the snow look a little warmer. That will be a conversation piece labrador nor there are more projects lined up charge extra the next time, yet this red is too red and this is just a 5 minutes job, it looks a bit empty, try to make everything bigger can you rework to make the pizza look more delicious. I know you've made thirty iterations but can we go back to the first one that was the best version we exceed the clients' expectations can you lower the price for the website? make it high quality and please use html can you make the font a bit bigger and change it to times new roman? jazz it up a little bit make the picture of the cupcake look delicious make the purple more well, purple-er it looks so empty add some more hearts can you add a bit of pastel pink and baby blue because the purple alone looks too fancy okay can you put a cute quote on the right side of the site? oh no it looks messed up! i think we need to start from scratch, can we have another option, for i was wondering if my cat could be placed over the logo in the flyer nor something summery; colourful. Can you put "find us on facebook" by the facebook logo? im not sure, try something else this was not according to brief i'll know it when i see it can't you just take a picture from the internet?. Make it original im not sure, try something else can you use a high definition screenshot for can we have another option can you make it look like this clipart i found. Theres all this spanish text on my site I know somebody who can do this for a reasonable cost I really like the colour but can you change it.

